%-------------------------
% Resume in Latex
% Author : Jake Gutierrez (Modified for Aleena Tahir)
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \small #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Aleena Tahir} \\ \vspace{1pt}
    \small Rawalpindi/Islamabad, Pakistan $|$ +92-310-596-8568 \\ 
    \small \href{mailto:aleenatahirf23@nutech.edu.pk}{aleenatahirf23@nutech.edu.pk} $|$
    \href{https://github.com/AleenaTahir1}{github.com/AleenaTahir1} $|$
    \href{https://www.linkedin.com/in/aleenatahir/}{linkedin.com/in/aleenatahir/} $|$
    \href{https://www.instagram.com/aleenaatahirr/}{instagram.com/aleenaatahirr/} $|$
    \href{https://wa.me/923105968568}{wa.me/923105968568} $|$
    \href{https://YOUR-PORTFOLIO-LINK-HERE}{Portfolio}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
\small{
Full Stack AI Engineer specializing in Agents and DevOps. I build heavy-lifting applications that are fast, smart, and scalable. From AI-powered workflows to backend APIs and modern UIs, I handle the entire stack so you can focus on growth.
}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\resumeSubHeadingListStart
  \resumeItem{\textbf{Languages:} Python, TypeScript/JavaScript, Rust, Go}
  \resumeItem{\textbf{AI \& Agents:} n8n, LangChain, RAG, OpenAI API, Gemini, Ollama}
  \resumeItem{\textbf{Backend \& Data:} FastAPI, Supabase (Postgres), MongoDB, ChromaDB, REST APIs}
  \resumeItem{\textbf{Frontend:} React, Next.js, Tailwind CSS}
  \resumeItem{\textbf{DevOps:} AWS, Docker, CI/CD, GitHub Actions}
  \resumeItem{\textbf{Tools:} Git/GitHub, Linux, Vite}
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

  \resumeSubheading
    {Ccript Agency}{Remote}
    {Full Stack AI Engineer, Agents \& DevOps Specialist}{2025 -- Present}

  \resumeSubheading
    {Neuralogic}{Remote}
    {Full Stack AI Engineer, Agents \& DevOps Specialist}{2025 -- Present}

  \resumeSubheading
    {Ocryz Pvt Ltd}{Hybrid}
    {AI Developer Intern}{2025}

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

  \resumeProjectHeading
    {\textbf{Gig Synappix} $|$ \emph{FastAPI, React, AI Chatbot}}{2025}
  \resumeItemListStart
    \resumeItem{Built a full gig marketplace platform (hire/get hired) with a FastAPI backend, React frontend, and AI chatbot experience.}
  \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Hill Icon (Skardu Hotel Website)} $|$ \emph{Next.js, SEO, WhatsApp Integration}}{2025}
  \resumeItemListStart
    \resumeItem{Designed and developed the full website with custom branding, performance-focused UI, SEO, deployment, and WhatsApp booking flow.}
  \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{NUTECH 360\textdegree\ Virtual Tour} $|$ \emph{React, 360\textdegree\ Media, Deployment}}{2025}
  \resumeItemListStart
    \resumeItem{Delivered an immersive campus virtual tour platform with guided navigation features for events and visitors.}
  \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Scoutly (Automated Job Search Agent)} $|$ \emph{n8n, LLMs, Email Automation}}{2025}
  \resumeItemListStart
    \resumeItem{Automates job discovery by analyzing a CV with AI, searching platforms, and emailing curated summaries with relevant roles.}
  \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{OmniRecall (AI Knowledge Assistant)} $|$ \emph{Rust, RAG, Multi-LLM Providers}}{2025}
  \resumeItemListStart
    \resumeItem{Built a privacy-first desktop assistant with global hotkeys, Spotlight-style UI, local RAG over PDFs/code, and multi-provider LLM support.}
  \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Nami (Real-time Chat)} $|$ \emph{Rust}}{2025}
  \resumeItemListStart
    \resumeItem{Developed a secure, lightweight real-time chat app with media sharing and presence/status features.}
  \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Cropwise (Crop Disease Classification)} $|$ \emph{Python, CNNs, Flask}}{2025}
  \resumeItemListStart
    \resumeItem{Web app for crop disease prediction from leaf images using CNN-based classification; includes training pipeline and UI.}
  \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {National University of Technology (NUTECH)}{Islamabad, Pakistan}
    {Bachelor of Science in Artificial Intelligence -- CGPA: 3.88/4.00}{Aug 2023 -- Present}
  \resumeSubheading
    {Army Public School Saddar}{Peshawar, Pakistan}
    {FSc (Computer Science)}{Aug 2021 -- Jun 2023}
  \resumeSubheading
    {Frontier Corps Public School}{Peshawar, Pakistan}
    {Matriculation (Science)}{Aug 2019 -- Jun 2021}
\resumeSubHeadingListEnd

\end{document}
